---
title: "Cross Validation"
date: "11/12/2019"
output: github_document
---

```{r load packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

set.seed(1)
```

Lecture notes: Cross validation involves taking your dataset and splitting it into two datasets: training and testing datasets. "Training" = data to build your model. "Testing" = data to use to evaluate out-of-sample fit. 80/20 ratio is a good split, but it also depends upon your sample size.

You evaluate the two datasets using the root mean squared error (RMSE).

You will introduced randomness with your split data, so you should iterate splits so that you can generate multiple iterations of the the process to account for the randomness.

Cross validation - use `modelr` package for:  
  
- `add_predictions()` and `add_residuals()`  
- `rmse()`  
- `crossv_mc`  

```{r generate dataset}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

Our goal is to fit a line that goes smoothly through the curve of points.

```{r training and testing}
train_df <- sample_n(nonlin_df, 80)
test_df <- anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

```{r root mean squared error}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

```{r iterate data splits}
cv_df <- crossv_mc(nonlin_df, 100)
```

